---
title: "R Notebook"
output:
  html_document:
    df_print: paged
  html_notebook: default
  word_document: default
  pdf_document: default
---

Question 1:
Standardise the mail_sent_date column values to YYYY-MM-DD standard date format
```{r}
library(readxl)
Email_sent <- read_excel("D:/casestudyfordataanalystinternship (5) (1) (1)/Email_sent.xlsx", 
                         sheet = "Sheet4")
View(Email_sent)
library(questionr)
a=is.na(Email_sent$mail_sent_date)
sum(a)
Email_sent$mail_sent_date=gsub("00:00:00","", Email_sent$mail_sent_date)
Email_sent$mail_sent_date=gsub("-","/", Email_sent$mail_sent_date)
Email_sent$mail_sent_date=gsub("\\.","-", Email_sent$mail_sent_date)
Email_sent$mail_sent_date=gsub("/","-", Email_sent$mail_sent_date)
Email_sent$mail_sent_date=as.Date(Email_sent$mail_sent_date, format = "%Y-%m-%d")
View(Email_sent)
```
Question 2
In which Year maximum number of emails were sent to doctors? 
```{r}
Email_sent$Year=format(Email_sent$mail_sent_date, format = "%Y")
View(Email_sent)
a=table(Email_sent$Year)
barplot(a, col = "#D0FF00")

```
Comment:#Year 2014 and 2015 are the years in which maximum number of emails were sent to doctors. Although the number of emails sent in 2014 is slightly higher than that of 2015.

Question 3:
Write a query to get total fine paid per Office
```{r}
data_merge2=merge(Email_sent,data, by.x="name_first", by.y="first_name")
View(data_merge2)
sum(is.na(data_merge2$office))
sum(is.na(data_merge2$total_fine))
data_n=data_merge2[!duplicated(data_merge2),]
View(data_n)
sum(is.na(data_n$office))
sum(is.na(data_n$total_fine))
data_office=aggregate(x = data_n$total_fine,     
                              by = list(data_n$office),            
                              FUN = sum)   
data_office

```


Question 4:
Write a query to get the highest total fine and lowest total fine paid per state
```{r}
a=unique(data$state)
data$cash_fine=as.numeric(data$cash_fine)
data$online_fine=as.numeric(data$online_fine)
data$total_fine=data$cash_fine+data$online_fine
df=data.frame(data$state,data$total_fine)
View(df)
#library(dplyr)
#df %>%group_by(data.state) %>% top_n(1,data.total_fine)
library(data.table)
Highest_fine=setDT(df)[, .SD[which.max(data.total_fine)], by = data.state]
Lowest_fine=setDT(df)[, .SD[which.min(data.total_fine)], by = data.state]
data_merge=merge(Highest_fine,Lowest_fine, by.x="data.state", by.y="data.state")
data_merge
```
Question 5
Write a query to get the least 2 states that had to pay minimum 'online' fine 
```{r}
data_of=aggregate(x = data$online_fine,     
          by = list(data$state),            
          FUN = sum)   
data_of=data_of[order(data_of$x),]
data_of[c(1:3),]

```
Comment : State AK, ND and ME are the states which have paid the least minimum fine but here State AK has not paid any online fine 
So if we consider state AK then AK and ND are the states that have paid the minimum fine and
if we don't consider state AK then ND and ME are the states who have paid the least fine.

Question 6
Write a SQL query to find the number of doctors that contributed to the state having highest 'cash' fine
```{r}
data_cf=aggregate(x = data$cash_fine,             
                  by = list(data$state),          
                  FUN = sum)   
data_cf=data_cf[order(-data_cf$x),]
data_cf
data_cf[1,]
data$full_name <- paste(data$first_name, data$last_name)

data_doctor = subset(data, state == "CA")
unique(data_doctor$full_name)

```
Comment: 517 doctors have contributed to the state CA having highest cashfine.

Question 7
Get the top 5 average fine paid per state and category
```{r}
data$avg_fine=(data$total_fine)/2
View(data)
data_avg_state<- data[,c(1,2,3,4,5,6,16)] %>%     
  arrange(desc(avg_fine)) %>% 
  group_by(state) %>%
  slice(1:5)
data_avg_state

data_avg_category<- data[,c(1,2,3,4,5,6,7,16)] %>%              
  arrange(desc(avg_fine)) %>% 
  group_by(category) %>%
  slice(1:5)
data_avg_category

```


